A Study on Penguins: A Minimal Reproducible Example

### 2024-08-21 01_Example/Manuscript.qmd
Use YAML chunk options and avoid labels with underscores
Regarding underscores, see https://quarto.org/docs/authoring/cross-references.html

```{r t_test, echo=FALSE}

@@

```{r descriptive_statistics, echo=FALSE, results='asis'}

@@

```{r bill_length_comparison, echo=FALSE, fig.cap="Histogram with Scatter Plot of Bill Lengths by Sex"}

>>>>

```{r}
#| label: "t-test"
#| echo: false

@@

```{r}
#| label: "descriptive-statistics"
#| echo: false
#| results: "asis"

@@

```{r}
#| label: "bill-length-comparison"
#| echo: false
#| fig.cap: "Histogram with Scatter Plot of Bill Lengths by Sex"
